Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-06-25 paper.tex
Added new reference and example in introduction

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage[usenames, dvipsnames]{color}

@@

Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads. Knowing the effect upon the model of changes in the electrode or electrolyte would allow designers to anticipate circumstances that will affect the load seen by their circuits. Another appeal of a compact model stems from the fact that electrode characteristics are succinctly and objectively represented by the model parameters. These parameters enable direct comparison of different electrodes, or the change in electrode properties over time. For example, in \cite{Kane13} changes in chronically-implanted electrodes are observed but there is no standard quantitative way of presenting the changes. Similarly, while there is a good understanding of what represents safe exposure, a compact model with parameters permits the prediction of the safety of any given stimulus regime.~\cite{Merrill05}

@@

\section{Conclusion}
\label{sect:conclusion}
We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
We have measured how changing the concentration of PBS affects the parameters of this model.
We have drawn direct relationships with concentration and conductivity sufficient to predict interface characteristics at arbitrary dilutions of PBS.
We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
Using DC measurements we conclude that the concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations measured. We hypothesise that this is because the double-layer sets the effective concentration of ions those involved in the Faradaic reactions, in a localised volume surrounding each electrode.

@@

final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines. Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.

@@

\bibitem{ScottSingle2013}
    Jonathan Scott and Peter Single,
    ``Compact Nonlinear Model of an Implantable Electrode Array for Spinal Cord Stimulation (SCS)'',
    to be published in
    {\em IEEE Transactions on Biomedical Circuits and Systems},
    DOI: 10.1109/TBCAS.2013.2270179, 2013.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage[usenames, dvipsnames]{color}

@@

Having a compact model of an electrode in the appropriate electrolyte allows circuit designers to simulate their designs with valid loads.
{
    \color{blue}
For example, the authors of \cite{Ethier2011} are concerned with the impedance presented by their electrode loads, and calculate power efficiency of their circuits.
This value is affected by the load impedance assumed.
Nevertheless, it is clear that they do not have a good idea of, nor a good way to simulate with, the load truly presented by an electrode in vivo or in vitro.
}
Knowing the effect upon the model of changes in the electrode or electrolyte would allow designers to anticipate circumstances that will affect the load seen by their circuits.

Another appeal of a compact model stems from the fact that electrode characteristics are succinctly and objectively represented by the model parameters.
These parameters enable direct comparison of different electrodes, or the change in electrode properties over time.
For example, in \cite{Kane13} changes in chronically-implanted electrodes are observed but there is no standard quantitative way of presenting the changes.
Similarly, while there is a good understanding of what represents safe exposure, a compact model with parameters permits the prediction of the safety of any given stimulus regime.~\cite{Merrill05}

@@

\section{Conclusion}
\label{sect:conclusion}
We have used the parameters of a compact electrical model of an implantable electrode as a way of objectively comparing scenarios.
We have measured how changing the concentration of PBS affects the parameters of this model.
We have drawn direct relationships with concentration and conductivity sufficient to predict interface characteristics at arbitrary dilutions of PBS.
We found that the magnitude of the CPE element moves much more slowly with concentration whereas the resistance moved almost linearly.
Using DC measurements we conclude that the concentration of PBS has no effect on the onset of Faradaic conduction for the range of concentrations measured. We hypothesise that this is because the double-layer sets the effective concentration of the species involved in the Faradaic reactions, in a localised volume surrounding each electrode.

@@

The final model, including 205 lines of resistive mesh, is represented by a SPICE netlist comprised of 348 lines. Simulation of this model, using the freely available ngSpice circuit simulator, at 1000 frequencies takes approximately 1 second on a modern CPU.

@@

\bibitem{ScottSingle2013}
    Jonathan Scott and Peter Single,
    ``Compact Nonlinear Model of an Implantable Electrode Array for Spinal Cord Stimulation (SCS)'',
    to be published in
    \emph{IEEE Transactions on Biomedical Circuits and Systems},
    DOI: 10.1109/TBCAS.2013.2270179, 2013.

\bibitem{Ethier2011}
    Sébastien Ethier and Mohamad Sawan,
    ``Exponential Current Pulse Generation for Efficient Very High-Impedance Multisite Stimulation'',
    \emph{IEEE Transactions on Biomedical Circuits and Systems},
    vol.~5 no.~1, February 2011, pp30--38.
